A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Add FRAC abbreviation to list
Edit Discussion for Flow

@@

It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $Recommended_{plus}$ treatment with a higher grain yield the $Recommended$ treatments. 
However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
Furthermore, the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.
To aid in making these decisions, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.

The scope of the meta-analysis is limited to the timing of fungicide application and therefore we can not validate all the variables available in PowderyMildewMBM.
However our results validate the decision of the app developers not to recommend prophylactic fungicide applications.
If the powdery mildew is not observed in the crop the app advises the user to keep monitoring for disease.
<!-- Think about how to word this, that we are using this to validate the app: The findings of this meta-analysis confirm the recommendations that PowderyMildewMBM gives in most situations would be correct. -->
<!-- I am finding it difficult to say that our findings confirm recommendations of the app, given the app does not advise on early late or recommended spray timing AND we don't investigate the differences in yield mitigations under the variables in the app (growth stage and weather) [Paul]-->

Scouting the crop for powdery mildew might not be necessary during the warmer months of the season. 
Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March, which marks the beginning of autumn (Figure \@ref(fig:Figure2)).
Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary. 
Scouting at intervals greater than 12 - 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
More work is needed to understand when "late" fungicide applications are too late.

We estimate the costs of applying tebuconazole fungicide at \$4.18 AU ha^-1^, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019]. 
The meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$). 
These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU ha^-1^ for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU ha^-1^ if a follow-up application is made.
Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
*Podosphaera xanthii* is categorised by the Australian Fungicide resistance Action Committee (FRAC) as a "High risk" candidate to evolve fungicide resistance [@FRACrisk2019].
Evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
In cucurbits, *P. xanthii* evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001].
In cereal crops *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].

According to the Fungicide Resistance Action Committee (FRAC) it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance. 
At the time of writing, in Australia one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a Quinone outside inhibitor.
Quinone is required in cell metabolism and active in the mitochondrial complex III.
However FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and alternated with a fungicide from a different group [@Brent2007]. 
For mungbean, past experiments have shown some success with sulphur applications to control powdery mildew. 
Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.

To extend the time that a fungicide remains effective against the target pathogen, strategic use of the fungicide must be considered.
Excessive fungicide sprays by a single active increase the selection pressure on the pathogen to evolve resistance [@Brent2007]. 
If any strains of the pathogen with resistance to the fungicide are present in a population regular use of the fungicide will increase its proportion in the population. 
Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen. 
Integrated pest management practices focus on using only the required number of chemical control to protect the economic return. 
These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.

Advising use of fungicide for disease control to protect yields should also consider the harm it may do to symbiotic relationships with microbiota. 
While some nitrogen fixing symbiont show a level of tolerance to fungicides, all are detrimentally affected by increasing concentrations of fungicide leading to lower nodulation and biomass accumulation [@Ahemad2011, @Shahid2019]. 
Therefore if a grower is relying on inoculating with rhizobia to help meet the crops nitrogen requirements, untimely and excessive applications of a systemic fungicide for powdery mildew control may actually reduce yield.

## Future work
This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].

>>>>

  - short: FRAC
    long: Fungicide Resistance Action Committee

@@

It is important to note, the studies included in this meta-analysis may not reflect a "normal" mungbean season. 
All the included experiments were intentionally sown late in the season, from January through to as late as early March, to ensure powdery mildew infection (Figure \@ref(fig:Figure2)). 
While certain circumstances may force growers to sow mungbeans late, many may decide to fallow their fields instead of risking a powdery mildew epidemics and an early frost damaging the crop and yields.
Regardless, according to the Australian Mungbean Association sowing guide [@AMAplanting], mungbeans should not be sown later than January in the Darling Downs, the region where the majority of trials were undertaken.
If the planting guide is adhered to the mungbean would be at a lower risk of powdery mildew, reducing the requirement for fungicide applications. 
An example of this is if we inspect the six trials in which powdery mildew manifested 60 days or greater after planting (Trial references: AM1304, mung1819/01, mung1011/01, AM1303, AM1305 and BB1305). 
Of these trials, four directly compared single $Recommended$ fungicide applications and $Recommended_{plus}$ (AM1303, AM1305, BB1305 and mung1819/01), two of which (AM1305 and mung1819/01) produced at least one treatment $Recommended_{plus}$ treatment with a higher grain yield the $Recommended$ treatments. 
However, neither AM1305 or mung1819/01 neither contained $Recommended$ or $Recommended_{plus}$ treatments with higher mean yields than the no-spray control.
This indicating there is likely no benefit to applying two fungicide applications when the disease manifests later than 60 days into the growing season. 
Furthermore, the 2013 trials, Premer (AM1303), Goolhi (AM1305) Marys Mount (AM1304) and Millmerran (BB1305), reported a significant difference in powdery mildew severity between the fungicide treatments.
However, none of the trials showed a significant difference in grain yield between treatments [@Millmerran2013, @premer2013, @Marysmount2013, @goolhi2013]. 
Therefore, discretion is still required for if fungicide applications are necessary given the crop growth stage and forecast weather conditions.

Scouting the crop for powdery mildew might not be necessary during the warmer months of the season.
Data from the trials included in this experiment show regardless of crop sowing date, powdery mildew establishes on average in the month of March (Figure \@ref(fig:Figure2)), which marks the beginning of autumn in Australia.
Considering the results of the meta-analysis, weekly inspections would be ideal to ensure timely fungicide applications if necessary.
Scouting at intervals greater than 12 -- 13 days, might risk crop losses if a spray schedule does not commence within aforementioned the spray window.
More work is needed to understand when "late" fungicide applications are too late.

We estimate the costs of applying tebuconazole fungicide at \$4.18 AU ha^-1^, if fungicide is purchased at \$15 / L [@Simfendorfer2011] and applications cost are \$2 per hectare [@QueenslandGovernment2019]. 
This meta-analysis estimates average yield savings of between `r coef(PM_mv)[3]*1000` kg ha^-1^ ($Recommended$) and `r coef(PM_mv)[4]*1000` kg ha^-1^ ($RecommendedPlus$).
These average yield savings would save \$`r (coef(PM_mv)[3]*1000)` AU ha^-1^ for a single application at first sign and \$`r coef(PM_mv)[4]*1000` AU ha^-1^ if a follow-up application is made.
Lucrative returns such as these may tempt growers into applying fungicide to control diseases such as powdery mildew when they are unnecessary.
Excessive use of fungicides are highly likely to lead ongoing problems such as fungicide resistance.
The evolution of fungicide resistance can occur quickly, especially when spray schedules are not designed with potential fungicide resistance in mind.
Powdery mildew is one such group of fungal pathogens with an extensive track record of rapidly developing fungicide resistance.
*P. xanthii* is categorised by the Australian Fungicide Resistance Action Committee (FRAC) as a "High Risk" candidate to evolve fungicide resistance [@FRACrisk2019].
*P. xanthii* has evolved resistance to benzimidazole within three years of its registration [@Peterson1973] and has evolved resistance to numerous fungicide classes, such as benzimidazoles, demethylation inhibitors, organophosphates, hydroxypyrimidines, quinone inhibitors and quinoxalines since [@Mcgrath2001] in cucurbits.
In cereal crops, *Blumeria graminis* showed reduced sensitivity to strobilurins in 1998, two years after the fungicides began being used in Europe [@Chin2001].

According to FRAC it is important to alternate or mix fungicides with different modes of action to avoid fungicide resistance.
At the time of writing, in Australia, only one fungicide is registered with the to treat powdery mildew in mungbean, Veritas/Custodia (200 g/L tebuconazole with 120 g/L azoxystrobin).
This fungicide provides dual action: tebuconazole disrupts C-14 demethylase, required in sterol biosynthesis for cell membranes; and azoxystrobin, a quinone outside inhibitor.
Quinone is required in cell metabolism and active in the mitochondrial complex III.
However, FRAC recommends that applications of QoIs or strobilurins, singularly or as a mixture, should not be applied consecutively and should be alternated with a fungicide from a different group [@Brent2007].
For mungbean, past experiments in the Northern Grains Region have shown some success with sulphur applications to control powdery mildew.
Sulphur is a non-systemic protectant and thus provides an excellent option for rotation to limit the emergence of fungicide resistance.

To extend the time that a fungicide remains effective against the target pathogen, the strategic use of the fungicide must be considered.
Excessive fungicide sprays with a single active ingredient increase the selection pressure on the pathogen to evolve resistance [@Brent2007].
If any strains of the pathogen with resistance to the fungicide are present in a population, regular use of the fungicide will increase its proportion in the population.
Therefore, managing the disease with fungicides for the highest economic return is likely not to require eradication of the causal pathogen.
Integrated pest management practices focus on using only the required number of chemical control to protect the economic return.
These strategies permit the presence of yield limiting diseases and pests if intervening would cost more than the economic return of protection.

To aid in making these decisions and devising a good strategy, DSS tools such as the PowderyMildewMBM consider crop growth stage and weather, to assist decision making whether to spray or not to spray [@Diggle] and can help users make an informed decision.
Using these sorts of tools can reduce unnecesary and unprofitable fungicide applications, which may help lead to the development of fungicide resistance.

<!-- I removed the part about inoculating mungbeans. This isn't common. They're lazy. Growers sometimes even look at adding N for them. I could be possibly persuaded to reinsert this section but it doesn't really fit the flow here, I don't think. If we need more text we might weave it in somehow. -->

## Future Work

This meta-analysis provides a ballast for the direction of future powdery mildew research in mungbean. 
However it does not provide enough certainty to when late fungicide applications would be too late to protect yield losses due to the disease. 
Future experiments should take note of physiological maturity of the crop throughout the season so "crop age" might be considered as a covariate in future analyses.
In cases where mungbean physiological maturity may not have been recorded the APSIM mungbean module [@RobertsonAPSIMlegume2002].
